---
title: "County Aggregations"
author: "asmtry"
output: html_document
---
  
```{r setupKnitr, include = FALSE}
knitr::opts_knit$set(echo = TRUE, root.dir = normalizePath('../'), warning = TRUE, collapse = TRUE)
#knitr::opts_chunk$set(cache=TRUE)
```

This worksheet leans heavily on `tidyverse` packages.

```{r setupEnv, include=FALSE}
source("R/utilities.R")

pkgTest("tidyverse", "lubridate", "tools", "readr")
```

In the previous steps we:

* 
*

```{r importData}
# # TODO: Remove readr::type_convert(), once CDL_Kc_LUT_daily isnt written with factors
# kc.index <- readRDS("output/tables/CDL_Kc_LUT_daily.rds")[,1:2] %>%
#   mutate_all(as.character) %>%
#   type_convert

cdl.index <- read_csv("input/TABLES/cdl_crops.csv")
cwu.master <- readRDS("output/cwu_master.rds")
yield.master <- read_csv("output/yields/NASS_summarized_bycounty.csv")
```


# Perform the WF calculation 

## By calendar year
```{r}
cwu.master.cyear <- cwu.master %>%
  group_by(crop, county, year = year(date)) %>%
  summarize_at(vars(cwr, ppt, et.b, et.g), funs(sum(., na.rm = TRUE)))

wf.master.cyear <- yield.master %>%
  inner_join(cwu.master.cyear, by = c("cdl.value" = "crop", "roi.index" = "county", "Year" = "year")) %>%
  mutate(wf.b = (et.b / prod.tonne)) %>%
  mutate(wf.g = (et.g / prod.tonne)) %>%             
  write_csv("output/wfs/wf_total_cyr.csv") %>%
  write_rds("output/wfs/wf_total_cyr.rds", compress = "gz")
```

## By water year
```{r}
cwu.master.wyear <- cwu.master %>%
  group_by(crop, county, year = year(waterYearlt(date))) %>%        # Create water year grouping
  filter(n_distinct(date) == 365 | n_distinct(date) == 366) %>%     # Filter for only complete years
  summarize_at(vars(cwr, ppt, et.b, et.g), funs(sum(., na.rm = TRUE)))

wf.master.wyear <- yield.master %>%
  inner_join(cwu.master.wyear, by = c("cdl.value" = "crop", "roi.index" = "county", "Year" = "year")) %>%
  mutate(wf.b = (et.b / prod.tonne)) %>%
  mutate(wf.g = (et.g / prod.tonne)) %>%             
  write_csv("output/wfs/wf_total_wyr.csv") %>%
  write_rds("output/wfs/wf_total_wyr.rds", compress = "gz")
```

## Save results

Note that we are explicitly casting categorical variables into the proper data type. We do this now, since
we are going to be passing these modeling results to the visualization and analysis routines, which can perform
specialized operations on 

## Inspecting discrepancies
Confused why the number of observations in the wf table is so much dramatically smaller (by ~50%) than the yield
observations table? Well, there are many entries for crops harvested in counties that were not observed
in the landcover dataset for that particular year. This is simply due to deficiencies in the land cover data set
(in this case, the CDL).

For example, the CAC records report lettuce harvests for every year from 2007 through 2016. However, the CDL
data set does not report any pixels of lettuce landcover for 2007 and 2009 (including the double-crop lettuce
landcover categories). There are many other entries with discrepancies, either due to:

* Missing observations in the yield or landcover datasets respectively. `Note`: The CDL dataset is the result
of supervised classification (specifically, a decision tree classifier), whereas the CAC dataset is the result
of surveys. We can assume that the CAC dataset is more reflective of what is actually harvested and grown within
a region.
* Misallignments between the yield and landcover datasets. For example, in Imperial county, sweet corn does not
appear in the landcover datasets until 2011, however it is present in the harvest records every year, and unspecified
corn is present in the landcover datasets every year. One attempt to reconcile data sets would be to aggregrate all
types of corn into one category.

To inspect this a bit deeper, we can use `dplyr::anti_join()`, which only displays entries in x (`yield.master`)
that **don't** have a matching entry in y (`cwu.master...`).

```{r, eval=FALSE, include=FALSE}
# t1 <- anti_join(yield.master, cwu.master.cyear, by = c("cdl.value" = "crop", "roi.index" = "county", "Year" = "year"))
# 
# cwr.master <- readRDS("output/cwr_master.rds") # Not needed, but including for inspecting
# t2 <- cwr.master %>%
#   filter(county == 13) %>% 
#   group_by(crop, county, year = year(date)) %>%
#   summarize(sum = sum(zsum)) %>%
#   left_join(cdl.index, by = c("crop" = "value"))
```

