---
title: "County Aggregations"
author: "asmtry"
output: html_document
---
  
```{r setupKnitr, include = FALSE}
knitr::opts_knit$set(echo = TRUE, root.dir = normalizePath('../'), warning = TRUE, collapse = TRUE)
knitr::opts_chunk$set(cache=TRUE)
```

This worksheet uses `tidyverse` packages, heavily.

```{r setupEnv, include=FALSE}
source("R/utilities.R")

pkgTest("tidyverse", "rgdal", "lubridate", "tools")
```

# Meta-data (units)
In our `YIELDS` directory, we inport county-level crop yield data, collected from the 
County Agricultural Commissioners’ (USDA/NASS). Hereafter, this dataset will be referred to as `yield.master`,
since this table contains yields, and the yields could be sourced from anywhere (not just USDA/NASS/CAC).

The data used in this worksheet can be found at the following URL, (as of June 2017):
https://www.nass.usda.gov/Statistics_by_State/California/Publications/AgComm/Detail/

From the USDA/NASS PDF reports:
> Values are recorded for all products grown during the calendar year, regardless of when they are marketed.

From the USDA/NASS reports, *most* production units are expressed in mass units, specifically 
(short) Tons US (2000 lbs). When tonnes (metric) are used in  NASS reorts, I've seen them explicitly 
specified as 'metric tons'. Other production units include: "Lbs/LBS/lbs" (pounds US), "Cwt/CWT/cwt" 
(hundredweight, aka 100 pounds US), "Col/COL/col" (colonies, for apiary production 🐝), 
"Each/EACH/each" (units, for certin products such as bee nuclei, queen bees, and turkey eggs for hatching), 
"Cord/CORD/cord" (volumetric unit for timber) and "Thou/THOU/thou" (thousands of units, for nursery plants).

Area units are in *US survey acres*, based on the square survey foot (NBS Special Publication 447, NIST Handbook 44 - 2012). 
Differences between the survey acre and the international acre are <2ppm (wikipedia::acre, NIST Handbook 44 - 2012). 
When hectares are used in NASS reports, I've seen them explicitly specified as 'hectares'.

Yield units are reported as (production mass)/(harvested acre). Specifically, yields are expresed as short tons per acre.

All of the above♪ is also detailed in USDA/ERS Agricultural Handbook Number 697 *"Weights, Measures, and Conversion 
Factors for Agricultural Commodities and Their Products"*. This document also provides conversion factors for unusual
commodity weights and measures (eg. carton, bushel, sack, barrel, lug) that we (luckily) don't have to use.

## CDL Quirks

Some quirks that you may notice in the CDL data set:

* Inconsistent capitalization in the `Unit` field (LBS vs Lbs vs lbs)
* Typos in the `County` field ("State Total" vs "State Totals" and "San Luis Obisp" vs "San Luis Obispo")
* Typos in the `Commodity Name` field ("CATTLE CALVES EXCLUDED UNSPECIFIE" vs "CATTLE CALVES EXCLUDED UNSPECIFIED"
  and "NURSERY HORTICULTRAL SPECIMIN MIS" vs "NURSERY HORTICULTRAL SPECIMIN MISC." and others)

## Import data and set constants

```{r importData}
yield.dir <- "input/YIELDS"
kc.index <- readRDS("output/tables/CDL_Kc_LUT_daily.rds")[,1:2]
kc.lut <- readRDS("output/tables/CDL_Kc_LUT_daily.rds")
cdl_nass <- read_csv("output/tables/CDL_NASS.csv")
counties <- readOGR("input/SHAPEFILES/cnty24k09_poly/cnty24k09_poly_simple.shp")
counties.index <- counties@data %>%
  mutate_all(as.character) %>%
  type_convert
```

If you end up doing lots of unit conversions, it may make sense to use a dedicated library/package,
but luckily, the harvested crops that we are interested in are only reported in US tons (short tons).
It's easier for me to verify the calculations on paper if everything is in SI units, so let's define
some conversion factors here, for later use.

All conversion factors are from the USDA/ERS Agricultural Handbook Number 697 *"Weights, Measures, 
and Conversion Factors for Agricultural Commodities and Their Products"*.

I really like the `udunits2` and `units` packages, along with the UNIDATA library that they depend on. 
```{r}
# TODO: Use units/udunits2/UNIDATA
# Short tons (US) to tonnes (metric tons)
conv <- list( ton = list(ton = 1, kg = 907.18474, tonne = 0.90718474),
              lb  = list(lb = 1, kg = 0.45359237, tonne = 0.00045359237),
              cwt = list(cwt = 1, lb = 100, kg = 45.35924, tonne = 0.045359237)
)
```


# Import and prepare yield and county data

Note that by defailt, the attribute table is read with R data frame conventions, thatis, coercing to
factors whenever possible. You can use `readr::type_convert` to run `readr`'s type-guessing logic on 
existing data frames. 
```{r prepareAnalysis_rds}
yield.paths <- list.files(path=yield.dir, pattern=".(csv)$", full.names=T)

yield.master <- do.call("rbind", lapply(yield.paths, read_csv, 
                                        col_types = cols(`Harvested Acres` = col_number(), 
                                                         Value = col_number())))

rm(yield.dir, yield.paths)

# Make the `Units` column lowercase to make things consistent
yield.master[["Unit"]] <- tolower(yield.master[["Unit"]])

counties.index <- counties@data %>%
  mutate_all(as.character) %>%
  type_convert
```

# Explore unique values in harvest dataset

## Unique crop categories
Here, we create `common.crops`, which is a character vector of the crop names that have an entry in *all* of the 
yearly crop reports. In other words, if there's a crop name category that is present in 2005-2011, but not present 
in 2012, then we will ignore that particular crop. 

We're only checking this becaue the length of the unique crop names differs from year to year, suggesting that 
some categories are present some years, and some aren't present other years. That said, having an entry does not
guarentee that there were any harvested acres that year. In other words, a year may have an entry for a crop that
did not have any harvested acres (which, is expected).


```{r prepCommonCrops_vis}
# Calc number of unique crop categories each year
yield.master %>%
  group_by(Year) %>%
  summarize(unique = length(unique(`Crop Name`)))

# Find the crop categories that are present in all years
# (Inner join across all categories)
yield.master %>%
  group_by(Year) %>%
  distinct(`Crop Name`)
```

The key operation is `dplyr::intersect()` (find which members of "Crop Name" are in common) which can be thought of 
as a SQL inner join. First, we produce a list of unique (`dplyr::distinct`) crop names by-year, then we intersect the 
list of names (performing the inner join).

```{r prepCommonCrops}
# TODO: For fun, figure out how to do this using just one (compound) statement using dplyr::inner_join()
common.crops <- yield.master %>%
  group_by(Year) %>%
  distinct(`Crop Name`) %>%
  summarize(cropname = list(`Crop Name`)) %>%
  select(cropname) %>%
  lapply(function(x) {(x)})

common.crops <- Reduce(intersect, common.crops[["cropname"]])
all.crops <- unique(unique(yield.master[["Crop Name"]]))
```

Note the crops that were removed. We may want to look at these in more detail later. epecially for categories
like "CORN WHITE", or "BEANS SNAP PROCESSING", and "TARO ROOT" (who knew that CA produced taro).

```{r prepCommonCrops2_vis}
# TODO: Investate the mass of the crops that weren't harvested every year
all.crops[!(all.crops %in% common.crops)]
```

## Unique ROI categories

We also have to allign the regions of interest (ROI) in our landcover dataset to our harvest dataset. Remember that
we partitioned the CWU calculation into ROIs based on counties, since harvest yields are reported at the county-scale.

Now, we have to make sure that the county categories that we used for the spatial partitioning (from our political
border shapefile) allign with the county categories used in the harvest yield reporting. We will also construct a 
look-up table.

Luckily, the CAC county names match up perfectly with the shapefile metadata, aside from a typo or two.


```{r prepCACcounty}
# Which counties in the harvest dataset ARE NOT present in the ROI index?
unique(yield.master$County)[which(!(unique(yield.master$County) %in% counties.index$NAME_PCASE))]

# Fix the typos
# WARNING: HARDCODED VALUES
yield.master <- yield.master %>%
  mutate(County = replace(County, County == "San Luis Obisp", "San Luis Obispo")) %>%
  mutate(County = replace(County, County == "State Total", "State Totals"))
```


# Associate yield ROIs and crop categories with landcover ROIs and crop categories

## Associate counties from harvest record with landcover ROIs
Here, we use `dplyr::inner_join` to join the county identifiers, (`counties.index["NUM"]`s  to the CAC master table, 
by matching county names.

```{r}
# Merge county identifiers
yield.master <- yield.master %>%
  left_join(counties.index[c("NAME_PCASE", "NUM")], by = c("County" = "NAME_PCASE")) %>%
  rename(roi.index = NUM) %>%
  mutate(roi.index = replace(`roi.index`, County == "Sum of Others", 991)) %>%
  mutate(roi.index = replace(`roi.index`, County == "State Totals", 999))
  
# TODO: TEST: Did the join operation work properly?
#setdiff(t1[sample(nrow(t1), 100),][c("County", "roi.index")], counties.index[c("NAME_PCASE", "NUM")] )
#t1[sample(nrow(t1), 100),][["roi.index"]] %in% counties.index[["NUM"]]
```

## Associate harvested crops with CDL crops

## Summarize harvested acres statewide for comparison with landcover areas
Here, we generate a list harvested acres for all years, for all counties (`County Code == 999`). 
We save this file as `NASS_acres_state.csv`

The key operation is `dplyr::outer_join()`, an operation that can be thought of as the union set.

```{r exportCommonCrops_untidy, eval=FALSE, include=FALSE}
# 'Untidy' use of R/tidyverse packages
# TODO: For fun, figure out how to do this using just one (compound) statement.
acres.state.master <- yield.master %>%
  filter(`County Code` == 999) %>%
  select(Year, `Crop Name`, `Commodity Code`, `Harvested Acres`) %>%
  group_by(Year) %>%
  nest() %>%
  select(data) %>%
  lapply(function(x) {(x)})

acres.state.master <- Reduce(function(...) full_join(..., by=c('Crop Name', 'Commodity Code')), acres.state.master[["data"]])

# WARNING: Hardcoded years
colnames(acres.state.master) <- c("Crop Name", "Commodity Code", 2007:2015)
# Order by Crop Name
acres.state.master <- acres.state.master[order(acres.state.master$`Crop Name`),]
# Write to csv
write_csv(acres.state.master, "output/yields/NASS_acres_state.csv")
```

Why did we care about harvested acres? It serves as a point of comparison, and allows us to see if the acres harvested 
align with the acres planted, as identified by CDL. We do this comparison in the `21.validation` worksheet.

NOTE: We are fortunate that the CAC data set includes harvested acres. Don't expect all yield reports from
other regions to include harvested acres.

NOTE: I dropped the typos in Crop Name when manually reconciling CDL and CAC categories.
TODO: Maybe create logic for flagging instances when a commodity code is mapped to more than one commodity name
      (which is what happened for "CATTLE CALVES...", "NURSERY FLOWER..." and etc.).

## Perform crop-category association

For now, we **manually** reconciled the USDA/NASS production categories to the CDL classes, using a pairing similiar to
that used by Fulton et al. 2012 (Appendix 2), where they related the County Agricultural Commissioners’ Production
Data Commodity Descriptions to "PI Codes" (Where PI likely refers to "Photo Identifier"). This manually-annotated
table is found under `output/tables/CDL_NASS.csv`. Let's import it and create a lookup table.

Here, we use `dplyr::inner_join` to join the `cdl_value`s and the `cdl_name`s to the CAC master table, by matching
`Commodity Code`s.

```{r assignYieldLandcover}
# Import if it hasn't been done already
# WARNING: Hardcoded path
cdl_nass <- read_csv("output/tables/CDL_NASS.csv")

yield.lc.master <- yield.master %>%
  left_join(cdl_nass[c("Commodity Code", "cdl_value", "cdl_name")], by = "Commodity Code") 

yield.lc.harvested <- yield.lc.master %>%
  filter(!is.na(cdl_value) & !is.na(Production))

yield.lc.excluded<- yield.lc.master %>%
  filter(is.na(cdl_value) | is.na(Production))
```

We just excluded crops that had a missing landcover index (`cdl_values`) **and** no reported yield (`Production`). 
Therefore, the entries that we excluded had either missing `cdl_values` **or** missing `Production`.

## Clean up unit names (CAC-specific)

At least for the CAC harvest dataset, the `Unit` field had some formatting inconsistency. Removing the non-harvested
crops seems to have left only one type of production unit
```{r}
unique(yield.lc.harvested["Unit"])
```

`NA` values are found in the entries for `State Totals` or `Sum of Others`, which are expressed in the same units as
the entries for each county. Let's just coerce all units to tons (after a quick sanity check).

```{r}
# WARNING: Hardcoded units
yield.lc.harvested <- yield.lc.harvested %>%
  mutate(Unit = "ton")
```


# Summarize harvest data by regions of intereste

Now, let's summarize harvest data by categories and prepare for exporting into our next step. Here is where
one of the larger assumptions are made:

* Assumption: our mapping of crops from the harvest data to our landcover classes and crop coefficient classes 
is somewhat accurate. For example, it's reasonable to map `BERRIES BLACKBERRIES` and `BERRIES RASPBERRIES` into 
a general *'Caneberries'* category, since we can expect them to have similar growing characteristics, and the 
landcover dataset does not discriminate between different types of caneberries. Ideally, we would like to be 
able to discriminate between different caneberries *and* have a crop growth model for each type of plant.
* Assumption: There is no "double-counting" of harvested crop mass between similar crop categories. For example, 
if we combine `PEACHES CLINGSTONE`, `PEACHES FREESTONE`, and `PEACHES UNSPECIFIED` into a general *'Peaches'* 
category, then we wouldn't expect any double counting. What about `CELERY FOOD SERVICE`, `CELERY FRESH MARKET`,
and `CELERY UNSPECIFIED`? Well, if a region reports celery harvested for the fresh market, it wouldn't also be reported
food service sale. The same goes for other commodities. Cotton has a few categories:`COTTON LINT PIMA`, 
`COTTON LINT UNSPECIFIED`, `COTTON LINT UPLAND`, `COTTON SEED PLANTING`, and `COTTONSEED`. We wouldn't expect the 
same biomass to get counted multiple times as lint, planting seed, and cottonseed.

## Summarize harvested weight

So, now let's add up all of the production amounts within each county, by commodity, by year. For the county
tallies,we drop the categories that represent aggregrations of counties. For the statewide tally, we condition 
on the `State Totals`category.

```{r}
# WARNING: Hardcoded path
yield.lc.bycounty <- yield.lc.harvested %>%
  group_by(Year, cdl_name, cdl_value, roi.index, County) %>%
  filter(`County Code` != 991 & `County Code` != 999) %>% 
  summarise(prod.tons = sum(Production), val.usd = sum(Value), hvst.acres = sum(`Harvested Acres`)) %>%
  mutate(prod.tonne = `prod.tons` * conv[["ton"]][["tonne"]]) %>%
  rename(cdl.value = cdl_value, cdl.name = cdl_name) %>%             # TODO: Replace with consistent naming
  write_csv(., "output/yields/NASS_summarized_bycounty.csv")

yield.lc.bystate <- yield.lc.harvested %>%
  group_by(Year, cdl_name, cdl_value, roi.index, County) %>%
  filter(`County Code` == 999) %>% 
  summarise(prod.tons = sum(Production), val.usd = sum(Value), hvst.acres = sum(`Harvested Acres`)) %>%
  mutate(prod.tonne = `prod.tons` * conv[["ton"]][["tonne"]]) %>%
  rename(cdl.value = cdl_value, cdl.name = cdl_name) %>%             # TODO: Replace with consistent naming
  write_csv(., "output/yields/NASS_summarized_bystate.csv")


```












