---
title: "Verification"
author: "asmtry"
date: "April 25, 2018"
output: html_document
---

```{r setupKnitr, include = FALSE}
knitr::opts_knit$set(echo = TRUE, collapse = TRUE)
# knitr::opts_chunk$set(cache = TRUE, autodep = TRUE,
#                       cache.path = paste0('cache/',sub(".Rmd", "", knitr::current_input()),'/'),
#                       fig.path = paste0('figures/',sub(".Rmd", "", knitr::current_input()),'/'))
knitr::opts_chunk$set(fig.width=8, fig.asp = 0.618, warning = FALSE)
options(width = 120)
```

# Setup
This worksheet leans heavily on `tidyverse` packages.

```{r setupEnv, include=FALSE}
source("R/utilities.R")
source("R/kc.R")
source("R/eto.R")

pkgTest( "rgdal", "raster", "sf", 
         "tidyverse", "lubridate", "plotly",
         "tools", "parallel")
rasterOptions(progress = "text", tmpdir = "tmpdir")
# rasterOptions(todisk = TRUE)
# As of May 2018, this worksheet uses `sf` features of ggplot that are currently under development
# devtools::install_github("tidyverse/ggplot2")
# As of May 2018, this worksheet uses `stars`, a package that is currently under development
# devtools::install_github("r-spatial/stars")
# pkgTest repeated for the non-CRAN packages, because knitr breaks otherwise
pkgTest("ggplot2")
ggplot2::theme_set(theme_bw())
```

This worksheet provides a framework for sampling the calculated CWR corpus (crop
water requirement) for a given region of interest, or time period of interest.

## Input Parameters
`target.date.range` contains the date range for our period of interest. This 
should be defined as an interval in the smallest unit of time present the CWR corpus. 
E.g. for the California case study, CWR was computed at a daily time step. 
If we are interested in sampling the 2015 water year, we can provide the starting
and ending dates. Alternatively, we can specify a starting date and use `lubridate`
to compute the end date, given a duration.
`target.region` contains the region of interest by which to sample the ETC corpus.
This should be provided as a shapefile. Alternatively, you can use `sf` or `rgdal`
to select subset a region of interest out of a larger shapefile.

`cwr.dir` contains the path to the CWR rasters.
E.g. for the California case study, we link to the daily crop ET calculated in 
`5.cwu_calcs.Rmd`.
`ppt.dir` contains the path to the precipitation (aka ppt) rasters.
E.g. for the California case study, we link to the upscalled daily PRISM data.
`lc.dir` contains the path to the landcover rasters. This is used as the base 
on which to compute zonal sums (the zones are the crop types).
E.g. for the California case study, we link to the USDA/NASS CDL.
`kc.lut` contains a wide table of daily crop coefficients for each modeled crop,
arranged according to crop categories present in the USDA/NASS CDL.
`cdl.table` is a look-up table containing pairings between CDL value and CDL
class name. This includes all other non-crop land cover categories in the CDL.
`CDL.LUT.dual` is arranged identically to `kc.lut`. However, it only contains
crop coefficients for double-cropped landcover categories.

```{r importData}
target.date.range <- lubridate::interval(ymd("20141001"), ymd("20150930"))
target.region <- readOGR("input/validation/2018_delta_et/delta_service_area/delta_service_area_teale.shp")
cwr.dir <- "output/cwr_calcs"
ppt.dir <- "output/cleaned_inputs/PRISM_scaled_projected"
lc.dir <- "output/cleaned_inputs/CDL_CA_projected"
kc.lut <- readRDS("output/tables/CDL_Kc_LUT_daily.rds")
cdl.table <- read_csv("input/TABLES/cdl_classes_all.csv")
CDL.LUT.dual <- readRDS("output/tables/CDL_LUT_dualtagged.rds")
```

## Enumerate input parameters
```{r enumerateInputs}
enumerate_inputs <- function(target.dir, product_name, source_index, date_index) {
  tibble(abs_path = list.files(path = target.dir, pattern = ".(tif)$", full.names = TRUE, recursive = TRUE)) %>%
    mutate(source = flatten_chr(map(strsplit(file_path_sans_ext(abs_path),"/"), source_index))) %>%
    mutate(product_name = product_name) %>%
    mutate(date = ymd(flatten_chr(map(strsplit(file_path_sans_ext(abs_path),"/"), date_index)))) %>%
    mutate(wyear = date %m+% months(3)) %>%
    return
}

cwr.table <- enumerate_inputs(cwr.dir, "cwr", 2, 4)
ppt.table <- enumerate_inputs(ppt.dir, "ppt", 3, 5)

lc.table <- tibble(abs_path = list.files(path=lc.dir, pattern=".(tif)$", full.names=T, recursive=TRUE)) %>%
  mutate(source = flatten_chr(map(strsplit(file_path_sans_ext(abs_path),"/"),3))) %>%
  mutate(product_name = "cdl") %>%
  mutate(date = ymd(flatten_chr(map(strsplit(file_path_sans_ext(abs_path),"/"),5))))

## TODO: Add input validation logic
rm(cwr.dir, ppt.dir,lc.dir)
```

## Mask ROI
This does not take very long for a small shapefile. It took about 250 seconds on a
Nehalem (c.a. 2011) Xeon.
```{r maskROI}
zone.mask <- lc.table %>% 
  filter(date %within% target.date.range) %>%
  pull(abs_path) %>%
  raster %>%
  raster::crop(target.region) %>%
  raster::mask(target.region)

writeRaster(zone.mask, "output/validation/cdl2015_deltaET_mask.tif")
zone.mask <- raster("output/validation/cdl2015_deltaET_mask.tif")

cwr.subset <- cwr.table %>%
  filter(date %within% target.date.range) %>%
  pull(abs_path)

ppt.subset <- ppt.table %>%
  filter(date %within% target.date.range) %>%
  pull(abs_path)
```

# Tally crop water requirement and precipitation
For some reason, `raster::zonal` fails when `rasterOptions(time = TRUE)`.
It fails with:
> in as.POSIXct.default(time2) : 
> do not know how to convert 'time2' to class “POSIXct”
TODO: Figure out how to fix it.

It takes approximately 7 seconds to crop each day and produce a zone sums.
For a 365-day water year, it took 40 minutes to process on a Nehalem (c.a. 2011) 
Xeon (3.2 Ghz, one thread).
```{r tallyParameters}
make_zone_sum <- function(abs_paths, index_path, target_region) {
  abs_paths <- raster(abs_paths) %>%
  raster::crop(target_region)
  z.table = zonal(abs_paths, raster(index_path), function(x,...) sum(as.numeric(x), na.rm = TRUE), progress = "text")
  return(z.table)
}

Sys.time()
cwr.tally <- cwr.subset %>%
  map(function(x) make_zone_sum(x, "output/validation/cdl2015_deltaET_mask.tif", target.region)) %>%
  map(as.tibble) %>%
  Reduce(function(x, y) full_join(x, y, by = "zone"), .) %>%
  `colnames<-`(c("crop", seq(1,ncol(.)-1))) %>%
  gather(date, zsum, -crop) %>% 
  mutate(date = as.Date(as.numeric(date) - 1, origin = int_start(target.date.range), format="%Y-%m-%d")) %>%
  write_rds("output/validation/cdl2015_deltaET_cwr.rds")


Sys.time()
ppt.tally <- ppt.subset %>%
  map(function(x) make_zone_sum(x, "output/validation/cdl2015_deltaET_mask.tif", target.region)) %>%
  map(as.tibble) %>%
  Reduce(function(x, y) full_join(x, y, by = "zone"), .) %>%
  `colnames<-`(c("crop", seq(1,ncol(.)-1))) %>%
  gather(date, zsum, -crop) %>% 
  mutate(date = as.Date(as.numeric(date) - 1, origin = int_start(target.date.range), format="%Y-%m-%d")) %>%
  write_rds("output/validation/cdl2015_deltaET_ppt.rds")
Sys.time()
```

# Clean CWR/PPT zone sums
This section replicates logic from `8.zone_prep.Rmd` to ortanize and remove 
superfluous non-crop categories from the zonal sum tallies.

## Clean zone sums to split double-cropped categories into respective crops
There are some categories that represent two crop's worth of CWU in a respective 
year. While `5.cwu_calcs.Rmd` distinguishes the separate crops, the tally logic
does not.

Here where we create a function to re-tag dual cropped classes into their real 
classes, depending on the day of year.
```{r reassignDualCrop}
# SMALL HACK: Resolve for leap years by adding a 366'th day 
#             that has crop parameters equal to the 365th
# Instead of modeling Feb 29, we model Dec 31st twice
# TODO: We can make this more accurate by modeling Feb 28th twice,
#       or adding logic to extend the growing season by one day during leap years.
#       Nevertheless, late December and February conditions are typically similar.
CDL.LUT.dual <- cbind(CDL.LUT.dual,"366" = CDL.LUT.dual[["365"]])
CDL.LUT.dual <- gather(CDL.LUT.dual, "day_of_year", "real_value", 3:368, -cdl_name, convert = TRUE)

reassign_dualcrop <- function(crop, date) {
  real_value <- left_join(data.frame("crop" = crop, "date" = yday(date)), CDL.LUT.dual, by = c("crop" = "value", "date" = "day_of_year"))[["real_value"]]
  return(ifelse(is.na(real_value), crop, real_value))
}
```

## Clean zone sums to remove non-crop counts
When we computed zone sums, we used raw landcover rasters, which included land 
cover classificaitons that we were not interested in (urban, water, et al.)

Here, we create two functions that the do the following:
  1. Remove non-crop land cover category zone sums
  2. Identify the non-modeled *crops* present in the zone sum observations.
  These are crop categories observed in the landcover dataset that we did not 
  have crop coefficients for.
  
```{r cleanZoneSums}
# List landuse-zones present in our zonesums that are NOT present in our crop model table
# These zones are either other non-crop categories, or crops that we did not model
not.counted <- sort(unique(cwr.tally$crop)[!(unique(cwr.tally$crop) %in% kc.lut$value)])
# Pair with category names from cdl.table
not.counted <- cdl.table[cdl.table[["VALUE"]] %in% not.counted,]
# Print the non-modeled CROPS
not.counted[not.counted[["VALUE"]] %in% c(5, 26, 27, 31, 38, 71, 74, 231, 232, 233, 234, 238, 242, 244, 247, 250),]

cwr.tally <- cwr.tally %>%
  mutate(crop = reassign_dualcrop(crop, date)) %>%
  filter(!(crop %in% not.counted[["VALUE"]])) %>%
  write_rds("output/validation/cdl2015_deltaET_cwr_cleaned.rds")

ppt.tally <- ppt.tally %>%
  mutate(crop = reassign_dualcrop(crop, date)) %>%
  filter(!(crop %in% not.counted[["VALUE"]])) %>%
  write_rds("output/validation/cdl2015_deltaET_ppt_cleaned.rds")
```


# Compute CWR/PPT volumes
This section replicates logic from `8.zone_prep.Rmd` to convert zonal sum tallies
into volumes of crop water requirement and water precipitated over harvested areas.

## Remove scaling factors
We applied scaling factors of 100 to the evapotranspiration and precipitation rasters, 
AND to the crop coefficients. If $z_{1}$ is our cumulative scaling factor for *ET*:

$$
\begin{aligned}
\textrm{CWR} &\approx \textrm{ETo} \times \textrm{Kc} \\
\textrm{CWR} \times z_1 &= (100 \cdot \textrm{ETo}) \times (100 \cdot \textrm{Kc}) \\
\hline
z_1 &= (100 \times  100) = 100^2 \\
\end{aligned}
$$

Likewise, our scaling factor for *PPT* ($z_{2}$) is:

$$
\begin{aligned}
\textrm{ppt} \times z_2 &= \textrm{ppt} \times 100\\
\hline
z &= 100 \\
\end{aligned}
$$

Note that there is no error here. If you think $$z$$ for precipitation should be 
$$100^2$$, think about it a bit harder.

```{r removeScalingFactors}
# WARNING: Hardcoded scaling factors
z1 = 100*100
z2 = 100

cwr.master <- cwr.tally %>%
  mutate(zsum = zsum/z1)

ppt.master <- ppt.tally %>%
  mutate(zsum = zsum/z2)
```

## Convert depths into volumes
`{cwr,ppt}.master` both represent the sum of all of the daily depths of 
precipitation and crop evapotransporation 'observed' in all of the grid cells of 
each zone. We can turn this value into an actualvolume of water by multiplying 
the depth of water in each cell by the area of each cell. Since we use a uniform 
grid for the entire state, each cell has the same area. 

Via dimensional analysis:
$$
x\ \textrm{mm ET} \times \frac{30*30\ \textrm(m^2)}{cell} \times \frac{\textrm{m}}{1000 \ \textrm{mm}}= \frac{0.9 \cdot x\ m^3 ET}{cell}
$$

```{r convertMapUnitsToVol}
xy.res <- 30
z.unit <- 0.001 #Units are in milimeters = 0.001 meters

cwr.master <- cwr.master %>%
  mutate(vol = zsum * (xy.res^2) * z.unit)

ppt.master <- ppt.master %>%
  mutate(vol = zsum * (xy.res^2) * z.unit)
```

## Compute IWR and green-water ET
In order to partition the water footprint into a rain-fed and irrigated water 
component, we first need to calculate the irrigation water requirement.

The irrigation water requirement is equivalent to blue-water ET.
The rainfed component is equivalent to green-water ET.
This is all summarized in a master table that describes crop water **use** (cwu).

```{r aggregateCWU}
# WARNING: Hardcoded path
cwu.master <- cwr.master %>%
  select(crop, date) %>%
  mutate(cwr = cwr.master[["vol"]]) %>%
  mutate(ppt = ppt.master[["vol"]]) %>%
  mutate(et.b = pmax(0,(`cwr`-`ppt`))) %>%
  mutate(et.g = pmin(cwr,ppt)) %>%
  write_rds("output/validation/cdl2015_deltaET_master.rds", compress = "gz")
```