---
title: "Figures: 2008-2015 averages by county"
author: "asmtry"
output:
  html_document:
    css: base.css
    code_folding: hide
    theme: readable
    toc: true
    toc_depth: 2
    toc_float: true
---
  
```{r setupKnitr, include = FALSE}
knitr::opts_knit$set(echo = TRUE, root.dir = normalizePath('../'), collapse = TRUE)
knitr::opts_chunk$set(cache = TRUE, autodep = TRUE,
                      cache.path = paste0('cache/',sub(".Rmd", "", knitr::current_input()),'/'),
                      fig.path = paste0('figures/',sub(".Rmd", "", knitr::current_input()),'/'))
knitr::opts_chunk$set(fig.width=10, fig.asp = 1.218, warning = FALSE)
options(width = 120)
```

# Setup
This worksheet leans heavily on `tidyverse` packages.

```{r setupEnv, include=FALSE}
source("R/utilities.R")
pkgTest("ggedit", "ggalt", "ggrepel", "ggthemes", "gridExtra", "cowplot", "viridis",
        "tidyverse", "lubridate", "tools", "readr", "broom", "knitr", "kableExtra", "DT",
        "rgdal", "sf", "devtools")
# As of July 2017, this worksheet uses `sf` features of ggplot that are currently under development
devtools::install_github("tidyverse/ggplot2")
# pkgTest repeated for the non-CRAN packages, because knitr breaks otherwise
pkgTest("ggplot2")
ggplot2::theme_set(theme_bw())
```

## Import data

`cdl.table` contains relations between crops, their index number in the Cropland Data Layer,
and the corresponding name and index number in the FAO Indicative Crop Classification (ICC 1.1).

`roi.table` contains relations from the regions of interest used to aggregrate the WF, PPT, 
and CWU calculations performed in steps 8-10. Here, the relation is the attribute table from a
shapefile of California county political boundaries. Attributes include: county index, name, and
corresponding DWR hydrologic region.

`ca.counties` contains the shapefile, on which `roi.table` is based.

`ca.hr` contains the shapefile of DWR hydrologic regions, for California.

`wf.master.wyear` contains annual sums of cwr, ppt, etc, wf, and harvested tons/acres/USD 
aggregrated by crop, county, and water year. It only includes the counties that have corresponding 
entries in the County Ag Comissioners (CAC) annual yield reports. Counties that had modeled ag 
production, without an accompanying entry in the CAC annual reports were omitted.

`wf.master.cyear` contains the above, except aggregrated by calendar year (instead of water year). 
This data set includes the extra year of 2007.

`yield.master` contains all of the statistics reported by the CAC annual reports (production tons, 
harvested acres, value in USD), for the modeled crops.

```{r importData, message=FALSE, warning=FALSE, include=FALSE}
cdl.table <- read_csv("input/TABLES/cdl_crops.csv")
roi.table <- read_csv("input/SHAPEFILES/cnty24k09_poly/cnty24k09_poly_attributes.csv")
ca.counties <- read_sf("input/SHAPEFILES/cnty24k09_poly/cnty24k09_poly_s100.shp")
ca.hr <- read_sf("input/SHAPEFILES/dwr/dwr_hydrologic_regions.shp")
wf.master.cyear <- readRDS("output/wfs/wf_total_cyr.rds")
wf.master.wyear <- readRDS("output/wfs/wf_total_wyr.rds")
yield.master <- read_csv("output/yields/NASS_summarized_bycounty.csv")
```

# C1: Annual statewide water demand, by region

Here, we sum all tallied quantities of harvested acres, tons in production, and value (USD)
by county, over each calendar and water year.

Note: `readr` initially recognizes these fields as integers. Some of these are large. Some
yearly sums are too large for a 32-bit `<int>` so, we must be coerce them to double.
```{r calc1}
wf.master.bycounty.cyear <- wf.master.cyear %>%
  mutate(Year = as.Date(sprintf("%s-01-01", Year), format="%F")) %>%
  group_by(roi.index, County, Year) %>%
  summarize_at(vars(hvst.acres, prod.tons, val.usd), funs(sum(as.numeric(.), na.rm = TRUE))) %>%
  left_join(roi.table %>% select(NUM,`HR_NAME`),
            by = c("roi.index" = "NUM")) %>%
  ungroup() %>%         # I'm not sure what to think about the expicit `ungroup()`
  `attr<-`("year_type", "calendar") %>%
  `attr<-`("summary_type", "total")

wf.master.bycounty.wyear <- wf.master.wyear %>%
  mutate(Year = as.Date(sprintf("%s-01-01", Year), format="%F")) %>%
  group_by(roi.index, County, Year) %>%
  summarize_at(vars(hvst.acres, prod.tons, val.usd), funs(sum(as.numeric(.), na.rm = TRUE))) %>%
  left_join(roi.table %>% select(NUM,`HR_NAME`),
            by = c("roi.index" = "NUM")) %>%
  ungroup() %>%         # I'm not sure what to think about the expicit `ungroup()`
  `attr<-`("year_type", "calendar") %>%
  `attr<-`("summary_type", "total")

wf.master.byHR.wyear <- wf.master.wyear %>%
  left_join(roi.table %>% 
              select(NUM,`HR_NAME`),
            by = c("roi.index" = "NUM")) %>%
  mutate(Year = as.Date(sprintf("%s-01-01", Year), format="%F")) %>%
  group_by(`HR_NAME`, Year) %>%
  summarize_at(vars(hvst.acres, prod.tons, val.usd), funs(sum(as.numeric(.), na.rm = TRUE))) %>%
  ungroup() %>%
  `attr<-`("year_type", "water") %>%
  `attr<-`("summary_type", "total") %>%
  `attr<-`("summarized_by", "DWR-HR")
```

```{r calc2}
ca.counties.wy <- ca.counties %>%
  inner_join(wf.master.bycounty.wyear %>% 
              select(roi.index, Year, hvst.acres, prod.tons, val.usd),
            by = c("NUM" = "roi.index"))

# ca.hr.wy <- ca.hr %>%
#   inner_join(wf.master.bycounty.wyear %>%
#               group_by(`HR_NAME`, Year) %>%
#               summarize_at(vars(cwr, ppt, et.b, et.g, wf.b, wf.g), funs(sum(., na.rm = TRUE))),
#             by = c("HR_NAME" = "HR_NAME"))
  
```

```{r}
ca.counties.wy %>%
  ggplot() +
  geom_sf(mapping = aes(fill = hvst.acres), color = "white") +
  facet_wrap(~Year, ncol = 3, dir = "h") +
  scale_fill_viridis(name = "hvst acres", trans = "log", option = "viridis", 
                     labels = function(x) format(signif(x,1)/1, scientific = TRUE)) +
  labs(title = "Annual Harvested Acres by county for 2008 - 2015 water years",
       subtitle = "log10 scale")
```