---
title: "Untitled"
author: "asmtry"
date: "March 22, 2018"
output:
  word_document: default
  html_document: default
---

```{r setupKnitr, include = FALSE}
knitr::opts_knit$set(echo = TRUE, collapse = TRUE)
knitr::opts_chunk$set(cache = TRUE, autodep = TRUE,
                      cache.path = paste0('cache/',sub(".Rmd", "", knitr::current_input()),'/'),
                      fig.path = paste0('figures/',sub(".Rmd", "", knitr::current_input()),'/'))
#knitr::opts_chunk$set(fig.width=8, fig.asp = 0.618, warning = FALSE)
options(width = 120)
```

# Setup

This worksheet leans heavily on `tidyverse` packages.

```{r setupEnv, include=FALSE}
source("R/utilities.R")
pkgTest("ggedit", "ggalt", "ggrepel", "ggthemes", "gridExtra", 
        "cowplot", "viridis", "ggfittext", "treemapify",
        "tidyverse", "lubridate", "tools", "broom", "knitr", "kableExtra", "DT",
        "rgdal", "devtools")
ggplot2::theme_set(theme_bw())
```

```{r importData, message=FALSE, warning=FALSE, include=FALSE}
wf.master.wyear <- readRDS("output/wfs/wf_total_wyr.rds")
yield.master <- read_csv("output/yields/NASS_summarized_bycounty.csv")


```

# Using master table
## Tabulate # of unique CDL classes by county
```{r}
# Calculate # of unique cdl classes by county across entire data set
# Should return 57 values for 58 counties minus san francisco
ucdl.all.bcounty <- wf.master.wyear %>%
  group_by(County) %>%
  summarize("All Years" = n_distinct(cdl.name)) %>%
  arrange(`All Years`) %>%
  arrange(County)

# Calculate # of unique cdl classes by year across entire data set
# Should return 8 values (2008-thru-2015)
ucdl.all.byear <- wf.master.wyear %>%
  group_by(Year) %>%
  summarize(Total = n_distinct(cdl.name)) %>%
  arrange(Year) %>%
  spread(Year, Total)

# Calculate # of unique cdl classes across entire data set
# Should return 1 value
ucdl.all <- wf.master.wyear %>%
  select(cdl.name) %>%
  n_distinct()

ucdl.wyear <- wf.master.wyear %>%
  group_by(County, Year) %>%
  summarize(uniquecrops = n_distinct(cdl.name)) %>%
  spread(Year, uniquecrops) %>%
  arrange(County) %>%
  left_join(.,ucdl.all.bcounty, by = "County") %>%
  rbind(c("County" = "Total", ucdl.all.byear,"All Years" = ucdl.all))

kable(ucdl.wyear)
```

## Tabulate # of harvested acres by county
```{r}
# Calculate sum of harvested acres by county across entire data set
# Should return 57 values for 58 counties minus san francisco
uarea.all.bcounty <- wf.master.wyear %>%
  group_by(County) %>%
  summarize("All Years" = sum(`hvst.acres`, na.rm = TRUE)) %>%
  arrange(`All Years`) %>%
  arrange(County)

# Calculate sum of harvested acres by year across entire data set
# Should return 8 values (2008-thru-2015)
uarea.all.byear <- wf.master.wyear %>%
  group_by(Year) %>%
  summarize("Total" = sum(`hvst.acres`, na.rm = TRUE)) %>%
  arrange(Year) %>%
  spread(Year, Total)

# Calculate sum of harvested acres across entire data set
# Should return 1 value
uarea.all <- wf.master.wyear %>%
  select(`hvst.acres`) %>%
  sum(na.rm = TRUE)

uarea.wyear <- wf.master.wyear %>%
  group_by(County, Year) %>%
  summarize(totacres = sum(`hvst.acres`, na.rm = TRUE)) %>%
  spread(Year, totacres) %>%
  arrange(County) %>%
  left_join(.,uarea.all.bcounty, by = "County") %>%
  rbind(c("County" = "Total", uarea.all.byear,"All Years" = uarea.all))

kable(uarea.wyear)

ggplot(data.frame(x= 2008:2015, y=t(uarea.all.byear))) + geom_line(aes(x,y)) + xlab("Water Year") + ylab("Harvested Acres") + theme_bw()

```

# Using County Ag Comissioners' Reports
Read in `NASS_acres_state.csv`, which is generated in `9.yield_prep.Rmd`.
This file generates a list of harvested acres for all years, for all counties, 
for all commodity codes as specified by the CAC reports (were `County Code == 999`).
```{r}
acres.state.nass <- read_csv("output/yields/NASS_acres_state.csv") %>%
  select(`2008`:`2015`) %>%
  summarize_all(sum,na.rm = TRUE)
```

# Generate CDL-CAC relation table
Read in `common.acres.csv`, which is a manually generated file which contains
relations between the CAC commoditiy categories and the CDL landcover classes.
```{r}
read_csv("output/tables/CDL_NASS.csv") %>%
  filter(!is.na(cdl_name)) %>%
  mutate(`Crop Name` = str_to_title(`Crop Name`)) %>%
  group_by(`cdl_name`) %>%
  mutate(cac_classes = paste(`Crop Name`, collapse = ", ")) %>%
  distinct(cdl_name, cac_classes) %>%
  kable()
```