---
title: "Untitled"
author: "asmtry"
date: "March 22, 2018"
output:
  word_document: default
  html_document: default
---

```{r setupKnitr, include = FALSE}
knitr::opts_knit$set(echo = TRUE, collapse = TRUE)
knitr::opts_chunk$set(cache = TRUE, autodep = TRUE,
                      cache.path = paste0('cache/',sub(".Rmd", "", knitr::current_input()),'/'),
                      fig.path = paste0('figures/',sub(".Rmd", "", knitr::current_input()),'/'))
#knitr::opts_chunk$set(fig.width=8, fig.asp = 0.618, warning = FALSE)
options(width = 120)
```

# Setup

This worksheet leans heavily on `tidyverse` packages.

```{r setupEnv, include=FALSE}
source("R/utilities.R")
pkgTest("tidyverse", "lubridate", "tools", "broom", "knitr", "kableExtra", "DT",
        "rgdal", "devtools")
ggplot2::theme_set(theme_bw())
```

```{r importData, message=FALSE, warning=FALSE, include=FALSE}
wf.master.wyear <- readRDS("output/wfs/wf_total_wyr.rds") %>%
  mutate(wf.a = wf.b + wf.g)
yield.master <- read_csv("output/yields/NASS_summarized_bycounty.csv")
```

# Using master table
## Tabulate # of unique CDL classes by county
```{r}
# Calculate # of unique cdl classes by county across entire data set
# Should return 57 values for 58 counties minus san francisco
ucdl.all.bcounty <- wf.master.wyear %>%
  group_by(County) %>%
  summarize("All Years" = n_distinct(cdl.name)) %>%
  arrange(County)

# Calculate # of unique cdl classes by year across entire data set
# Should return 8 values (2008-thru-2015)
ucdl.all.byear <- wf.master.wyear %>%
  group_by(Year) %>%
  summarize(Total = n_distinct(cdl.name)) %>%
  arrange(Year) %>%
  spread(Year, Total)

# Calculate # of unique cdl classes across entire data set
# Should return 1 value
ucdl.all <- wf.master.wyear %>%
  select(cdl.name) %>%
  n_distinct()

ucdl.wyear <- wf.master.wyear %>%
  group_by(County, Year) %>%
  summarize(uniquecrops = n_distinct(cdl.name)) %>%
  spread(Year, uniquecrops) %>%
  arrange(County) %>%
  left_join(.,ucdl.all.bcounty, by = "County") %>%
  rbind(c("County" = "Total", ucdl.all.byear,"All Years" = ucdl.all))

kable(ucdl.wyear)
```

## Tabulate # of harvested acres by county
```{r}
# Calculate sum of harvested acres by county across entire data set
# Should return 57 values for 58 counties minus san francisco
all.area.county <- wf.master.wyear %>%
  group_by(County) %>%
  summarize("All Years" = sum(`hvst.acres`, na.rm = TRUE)) %>%
  arrange(`All Years`) %>%
  arrange(County)

# Calculate sum of harvested acres by year across entire data set
# Should return 8 values (2008-thru-2015)
year.area <- wf.master.wyear %>%
  group_by(Year) %>%
  summarize("Total" = sum(`hvst.acres`, na.rm = TRUE)) %>%
  arrange(Year) %>%
  spread(Year, Total)

# Calculate sum of harvested acres across entire data set
# Should return 1 value
all.area <- wf.master.wyear %>%
  select(`hvst.acres`) %>%
  sum(na.rm = TRUE)

year.area.county <- wf.master.wyear %>%
  group_by(County, Year) %>%
  summarize(totacres = sum(`hvst.acres`, na.rm = TRUE)) %>%
  spread(Year, totacres) %>%
  arrange(County) %>%
  left_join(.,all.area.county, by = "County") %>%
  rbind(c("County" = "Total", year.area,"All Years" = all.area))

kable(year.area.county)

ggplot(data.frame(x= 2008:2015, y=t(year.area))) + geom_line(aes(x,y)) + xlab("Water Year") + ylab("Harvested Acres") + theme_bw()
```

## Tabulate # of harvested acres by crop
```{r}
# Calculate sum of harvested acres by county across entire data set
# Should return 57 values for 58 counties minus san francisco
all.area.crop <- wf.master.wyear %>%
  group_by(cdl.name) %>%
  summarize("All Years" = sum(`hvst.acres`, na.rm = TRUE)) %>%
  arrange(cdl.name)

# Calculate sum of harvested acres by year across entire data set
# Should return 8 values (2008-thru-2015)
year.area <- wf.master.wyear %>%
  group_by(Year) %>%
  summarize("Total" = sum(`hvst.acres`, na.rm = TRUE)) %>%
  arrange(Year) %>%
  spread(Year, Total)

# Calculate sum of harvested acres across entire data set
# Should return 1 value
all.area <- wf.master.wyear %>%
  select(`hvst.acres`) %>%
  sum(na.rm = TRUE)

year.area.crop <- wf.master.wyear %>%
  group_by(cdl.name, Year) %>%
  summarize(totacres = sum(`hvst.acres`, na.rm = TRUE)) %>%
  spread(Year, totacres) %>%
  arrange(cdl.name) %>%
  left_join(.,all.area.crop, by = "cdl.name") %>%
  rbind(c("cdl.name" = "Total", year.area,"All Years" = all.area))

kable(year.area.crop)

#ggplot(data.frame(x= 2008:2015, y=t(year.area))) + geom_line(aes(x,y)) + xlab("Water Year") + ylab("Harvested Acres") + theme_bw()
```

## Plot
```{r}
year.area.crop <- wf.master.wyear %>%
  group_by(cdl.name, Year) %>%
  summarize(totacres = sum(`hvst.acres`, na.rm = TRUE))

year.area.crop %>%
  ggplot() + 
  geom_line(mapping = aes(x = Year, y = totacres, color = cdl.name))
```

# CWR
## Tabulate cwr by crop
```{r}
# Calculate sum of harvested acres by county across entire data set
# Should return 57 values for 58 counties minus san francisco
all.cwr.crop <- wf.master.wyear %>%
  group_by(cdl.name) %>%
  summarize("All Years" = sum(`cwr`, na.rm = TRUE)) %>%
  arrange(cdl.name)

# Calculate sum of harvested acres by year across entire data set
# Should return 8 values (2008-thru-2015)
year.cwr <- wf.master.wyear %>%
  group_by(Year) %>%
  summarize("Total" = sum(`cwr`, na.rm = TRUE)) %>%
  arrange(Year) %>%
  spread(Year, Total)

# Calculate sum of harvested acres across entire data set
# Should return 1 value
all.cwr <- wf.master.wyear %>%
  select(`cwr`) %>%
  sum(na.rm = TRUE)

year.cwr.crop <- wf.master.wyear %>%
  group_by(cdl.name, Year) %>%
  summarize(totacres = sum(`cwr`, na.rm = TRUE)) %>%
  spread(Year, totacres) %>%
  arrange(cdl.name) %>%
  left_join(.,all.cwr.crop, by = "cdl.name") %>%
  rbind(c("cdl.name" = "Total", year.cwr,"All Years" = all.cwr)) %>%
  mutate_all(funs(signif(.,3)))

kable(year.cwr.crop)
```

## Tabulate cwr by county
```{r}
# Calculate sum of harvested acres by county across entire data set
# Should return 57 values for 58 counties minus san francisco
all.cwr.county <- wf.master.wyear %>%
  group_by(County) %>%
  summarize("All Years" = sum(`cwr`, na.rm = TRUE)) %>%
  arrange(`All Years`) %>%
  arrange(County)

# Calculate sum of harvested acres by year across entire data set
# Should return 8 values (2008-thru-2015)
year.cwr <- wf.master.wyear %>%
  group_by(Year) %>%
  summarize("Total" = sum(`cwr`, na.rm = TRUE)) %>%
  arrange(Year) %>%
  spread(Year, Total)

# Calculate sum of harvested acres across entire data set
# Should return 1 value
all.cwr <- wf.master.wyear %>%
  select(`cwr`) %>%
  sum(na.rm = TRUE)

year.cwr.county <- wf.master.wyear %>%
  group_by(County, Year) %>%
  summarize(totacres = sum(`cwr`, na.rm = TRUE)) %>%
  spread(Year, totacres) %>%
  arrange(County) %>%
  left_join(.,all.cwr.county, by = "County") %>%
  rbind(c("County" = "Total", year.cwr,"All Years" = all.cwr)) %>%
  mutate_all(funs(signif(.,3)))

kable(year.cwr.county)

#ggplot(data.frame(x= 2008:2015, y=t(year.cwr))) + geom_line(aes(x,y)) + xlab("Water Year") + ylab("Harvested Acres") + theme_bw()
```

# WF
## Tabulate total WF by crop
```{r}
# Calculate sum of harvested acres by county across entire data set
# Should return 57 values for 58 counties minus san francisco
all.wfa.crop <- wf.master.wyear %>%
  group_by(cdl.name) %>%
  summarize("All Years" = sum(`wf.a`, na.rm = TRUE)) %>%
  arrange(cdl.name)

# Calculate sum of harvested acres by year across entire data set
# Should return 8 values (2008-thru-2015)
year.wfa <- wf.master.wyear %>%
  group_by(Year) %>%
  summarize("Total" = sum(`wf.a`, na.rm = TRUE)) %>%
  arrange(Year) %>%
  spread(Year, Total)

# Calculate sum of harvested acres across entire data set
# Should return 1 value
all.wfa <- wf.master.wyear %>%
  select(`wf.a`) %>%
  sum(na.rm = TRUE)

year.wfa.crop <- wf.master.wyear %>%
  group_by(cdl.name, Year) %>%
  summarize(totacres = sum(`wf.a`, na.rm = TRUE)) %>%
  spread(Year, totacres) %>%
  arrange(cdl.name) %>%
  left_join(.,all.wfa.crop, by = "cdl.name") %>%
  rbind(c("cdl.name" = "Total", year.wfa,"All Years" = all.wfa)) %>%
  mutate_all(funs(signif(.,3)))

kable(year.wfa.crop)
```

## Tabulate total WF by county
```{r}
# Calculate sum of harvested acres by county across entire data set
# Should return 57 values for 58 counties minus san francisco
all.wfa.county <- wf.master.wyear %>%
  group_by(County) %>%
  summarize("All Years" = sum(`wf.a`, na.rm = TRUE)) %>%
  arrange(`All Years`) %>%
  arrange(County)

# Calculate sum of harvested acres by year across entire data set
# Should return 8 values (2008-thru-2015)
year.wfa <- wf.master.wyear %>%
  group_by(Year) %>%
  summarize("Total" = sum(`wf.a`, na.rm = TRUE)) %>%
  arrange(Year) %>%
  spread(Year, Total)

# Calculate sum of harvested acres across entire data set
# Should return 1 value
all.wfa <- wf.master.wyear %>%
  select(`wf.a`) %>%
  sum(na.rm = TRUE)

year.wfa.county <- wf.master.wyear %>%
  group_by(County, Year) %>%
  summarize(totacres = sum(`wf.a`, na.rm = TRUE)) %>%
  spread(Year, totacres) %>%
  arrange(County) %>%
  left_join(.,all.wfa.county, by = "County") %>%
  rbind(c("County" = "Total", year.wfa,"All Years" = all.wfa)) %>%
  mutate_all(funs(signif(.,3)))

kable(year.wfa.county)

#ggplot(data.frame(x= 2008:2015, y=t(year.cwr))) + geom_line(aes(x,y)) + xlab("Water Year") + ylab("Harvested Acres") + theme_bw()
```

# Using County Ag Comissioners' Reports
Read in `NASS_acres_state.csv`, which is generated in `9.yield_prep.Rmd`.
This file generates a list of harvested acres for all years, for all counties, 
for all commodity codes as specified by the CAC reports (were `County Code == 999`).
```{r}
acres.state.nass <- read_csv("output/yields/NASS_acres_state.csv") %>%
  select(`2008`:`2015`) %>%
  summarize_all(sum,na.rm = TRUE)
```



# Generate CDL-CAC relation table
Read in `common.acres.csv`, which is a manually generated file which contains
relations between the CAC commoditiy categories and the CDL landcover classes.
```{r}
read_csv("output/tables/CDL_NASS.csv") %>%
  filter(!is.na(cdl_name)) %>%
  mutate(`Crop Name` = str_to_title(`Crop Name`)) %>%
  group_by(`cdl_name`) %>%
  mutate(cac_classes = paste(`Crop Name`, collapse = ", ")) %>%
  distinct(cdl_name, cac_classes) %>%
  kable()
```

# Generate CDL-FAO relation table
Read in `common.acres.csv`, which is a manually generated file which contains
relations between the FAO Indicative Crop Classification and the CDL landcover 
classes.
```{r}
read_csv("input/TABLES/cdl_crops.csv") %>%
  filter(!is.na(FAO_title)) %>%
  group_by(`FAO_title`) %>%
  mutate(FAO_crops = paste(`cdl_name`, collapse = ", ")) %>%
  distinct(FAO_title, FAO_crops) %>%
  kable()
```