---
title: "Delta ET Validation - Figures"
author: "asmtry"
date: "April 26, 2018"
output: html_document
---

```{r setupKnitr, include = FALSE}
knitr::opts_knit$set(echo = TRUE, collapse = TRUE)
# knitr::opts_chunk$set(cache = TRUE, autodep = TRUE,
#                       cache.path = paste0('cache/',sub(".Rmd", "", knitr::current_input()),'/'),
#                       fig.path = paste0('figures/',sub(".Rmd", "", knitr::current_input()),'/'))
knitr::opts_chunk$set(fig.width=8, fig.asp = 0.618, warning = FALSE)
options(width = 120)
```

# Setup
This worksheet leans heavily on `tidyverse` packages.
```{r setupEnv, include=FALSE}
source("R/utilities.R")
source("R/kc.R")
source("R/eto.R")

pkgTest("tidyverse", "lubridate", "readxl", "plotly", "ggthemes", "tools")
rasterOptions(progress = "text", tmpdir = "tmpdir")
# rasterOptions(todisk = TRUE)
# As of May 2018, this worksheet uses `sf` features of ggplot that are currently under development
# devtools::install_github("tidyverse/ggplot2")
# As of May 2018, this worksheet uses `stars`, a package that is currently under development
# devtools::install_github("r-spatial/stars")
# pkgTest repeated for the non-CRAN packages, because knitr breaks otherwise
pkgTest("ggplot2")
ggplot2::theme_set(theme_bw(base_size = 11))
```

## Import data

`cdl.table` contains relations between crops, their index number in the 
Cropland Data Layer, and the corresponding name and index number in the 
FAO Indicative Crop Classification (ICC 1.1).
`cwu.master` contains daily sums of cwr, ppt, etc, and harvested tons/acres/USD 
aggregated by crop, county, and water year. It only includes the counties that 
have corresponding entries in the County Ag Comissioners (CAC) annual yield 
reports. Counties that had modeled ag production, without an accompanying entry 
in the CAC annual reports were omitted.
`cdl.table` is a look-up table containing pairings between CDL value and CDL
class name. This includes all other non-crop land cover categories in the CDL.

```{r importData, message=FALSE, warning=FALSE, include=FALSE}
cdl.table <- read_csv("input/TABLES/cdl_crops.csv")
cwu.master <- read_rds("output/validation/cdl2015_deltaET_master.rds")
cdl.table <- read_csv("input/TABLES/cdl_classes_all.csv")
deltaET <- read_xlsx("input/validation/2018_delta_et/ModelResultsSummary.xlsx", sheet = "data")
```

## Prepare validation data
The Delta Consumptive Water Use Comparative Study uses 3-digit English shortname 
representations of month (e.g. JAN, FEB, etc.)
Here, we overwrite the locale environmental variables for time, to get 
reproducable behavior across platforms.
```{r prepValidation}
Sys.setlocale("LC_TIME", "C")
deltaET.wy2015 <- deltaET %>%
  filter(region == "dsa") %>%  # Region is delta service area (denoted by shapefile)
  filter(include == "yes") %>% # Removes landcover types not considered in delta study
  filter(wateryear == 2015) %>% 
  mutate(date = as.Date(paste0(month,"01",wateryear), format = "%b%d%Y")) %>%
  mutate(date = if_else(month(date) > 9, date %m+% years(-1), date)) %>%
  mutate(crop_acft = as.double(crop_acft))
```


# Summarize data

## Summarize model data
```{r summarizeData}
cwu.wy2015 <- cwu.master %>%
  mutate(wyear = date %m+% months(3)) %>%
  group_by(crop, year = year(wyear)) %>%
  summarize_at(vars(cwr, ppt, et.b, et.g), funs(sum(., na.rm = TRUE))) %>%
  inner_join(cdl.table, by = c("crop" = "VALUE")) %>%
  rename(cdl.name = CLASS_NAME) %>%
  select(year, crop, cdl.name, cwr, ppt, et.b, et.g) %>%
  dplyr::ungroup()

cwu.wy2015.month <- cwu.master %>%
  group_by(crop, date = floor_date(date, "month")) %>%
  summarize_at(vars(cwr, ppt, et.b, et.g), funs(sum(., na.rm = TRUE))) %>%
  inner_join(cdl.table, by = c("crop" = "VALUE")) %>%
  rename(cdl.name = CLASS_NAME) %>%
  select(date, crop, cdl.name, cwr, ppt, et.b, et.g) %>%
  dplyr::ungroup()


cwu.wy2015 %>%
 summarize_at(vars(cwr, ppt, et.b, et.g), funs(sum(., na.rm = TRUE)))
```

## Summarize validation data
```{r}
deltaET.wy2015.month <- deltaET.wy2015 %>%
  group_by(date, model, cropname) %>%
  summarize_at(vars(count, crop_acft), funs(sum(., na.rm = TRUE)))
```


# Figure: Monthly differences in modeled ETc
To convert from cubic meters to acre feet, use the following conversion factor:
$$
 m^3 \times \frac{\textrm{acre}}{4,046.87261\ m^2} \times \frac{\textrm{foot}}{0.3048\ m} = 8.104\times10^{-4}\ ^{AF}/_{m^3}
$$
```{r}
deltaET.wy2015.monthtot <- deltaET.wy2015.month %>%
  group_by(date, model) %>%
  summarize(tot_acft = sum(crop_acft))

cwu.wy2015.monthtot <- cwu.wy2015.month %>%
  group_by(date) %>%
  mutate(acft = cwr * 8.104 * 10^(-4)) %>%
  summarize(tot_acft = sum(acft)) %>%
  mutate(model = "manuscript") 
  
all.wy2015.monthtot <- deltaET.wy2015.monthtot %>%
  bind_rows(cwu.wy2015.monthtot) %>%
  ungroup() %>%
  mutate(model = fct_relevel(model, "manuscript", after = Inf))
```
## Combined
```{r}
all.wy2015.monthtot %>%
  filter(model != "eto") %>% # Drop ETo, since it's not a real crop model
  ggplot() +
  geom_col(aes(x = date, y = tot_acft, fill = model), position = "dodge") +
  scale_x_date(date_breaks = "1 month", date_labels = "%b", expand =  expand_scale(mult = c(0.03, 0.03))) +
  scale_y_continuous("Thousand Acre Feet", labels = function(x) x/1000,
                     breaks = seq(0,300*1000, by = 50*1000),
                     expand =  expand_scale(mult = c(0.02, 0.06))) +
  scale_fill_tableau("colorblind10") +
  coord_cartesian() +
  labs(title = "Water Year 2015 Monthly Estimated Crop Evapotranspiration",
         x = "Date", y = "Thousand Acre-feet", fill = "Model") +
  theme(legend.direction = "horizontal", legend.justification = c(0, 1), legend.position = c(0, 1),
    legend.background = element_rect(fill=alpha(0.4)))
```

## Faceted (model on axis)
```{r}
all.wy2015.monthtot %>%
  filter(model != "eto") %>% # Drop ETo, since it's not a real crop model
  mutate(month = month(date, label = TRUE, abbr = TRUE)) %>%
  ggplot() +
  geom_col(aes(x = model, y = tot_acft, fill = model), position = "dodge") +
  facet_grid(facets = . ~ month ) +
  scale_y_continuous("Thousand Acre Feet", labels = function(x) x/1000,
                     breaks = seq(0,300*1000, by = 50*1000),
                     expand =  expand_scale(mult = c(0.02, 0.06))) +
  scale_fill_tableau("colorblind10") +
  coord_cartesian() +
  labs(title = "Water Year 2015 Monthly Estimated Crop Evapotranspiration",
         x = "Model", y = "Thousand Acre-feet") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## Faceted (model in legend)
```{r}
all.wy2015.monthtot %>%
  filter(model != "eto") %>% # Drop ETo, since it's not a real crop model
  mutate(month = month(date, label = TRUE, abbr = TRUE)) %>%
  ggplot() +
  geom_col(aes(x = model, y = tot_acft, fill = model), position = "dodge") +
  facet_grid(facets = . ~ month ) +
  scale_y_continuous("Thousand Acre Feet", labels = function(x) x/1000,
                     breaks = seq(0,300*1000, by = 50*1000),
                     expand =  expand_scale(mult = c(0.02, 0.06))) +
  scale_fill_tableau("colorblind10") +
  coord_cartesian() +
  labs(title = "Water Year 2015 Monthly Estimated Crop Evapotranspiration",
         x = "Model", y = "Thousand Acre-feet") +
  guides(fill = guide_legend(direction = "horizontal", position = "bottom", nrow = 1)) +
  theme(axis.ticks = element_blank(), axis.text.x = element_blank(),
        legend.direction = "horizontal", legend.position = "bottom")
```