---
title: "Figures: 2008-2015 totals by county"
author: "asmtry"
output:
  html_document:
    css: base.css
    code_folding: hide
    theme: readable
    toc: true
    toc_depth: 2
    toc_float: true
---
  
```{r setupKnitr, include = FALSE}
knitr::opts_knit$set(echo = TRUE, root.dir = normalizePath('../'), collapse = TRUE)
knitr::opts_chunk$set(cache = TRUE, autodep = TRUE,
                      cache.path = paste0('cache/',sub(".Rmd", "", knitr::current_input()),'/'),
                      fig.path = paste0('figures/',sub(".Rmd", "", knitr::current_input()),'/'))
knitr::opts_chunk$set(fig.width=8, fig.asp = 0.618, warning = FALSE)
options(width = 120)
```

# Setup

This worksheet leans heavily on `tidyverse` packages.

```{r setupEnv, include=FALSE}
source("R/utilities.R")
pkgTest("ggedit", "ggalt", "ggrepel", "ggthemes", "gridExtra", "cowplot", "viridis",
        "tidyverse", "lubridate", "tools", "readr", "broom", "knitr", "kableExtra", "DT",
        "rgdal", "devtools")
install_github("wilkox/ggfittext")
install_github("wilkox/treemapify")
# pkgTest repeated for the non-CRAN packages, because knitr breaks otherwise
pkgTest("ggfittext", "treemapify")
ggplot2::theme_set(theme_bw())
```
## Import data

`cdl.table` contains relations between crops, their index number in the Cropland Data Layer,
and the corresponding name and index number in the FAO Indicative Crop Classification (ICC 1.1).

`roi.table` contains relations from the regions of interest used to aggregrate the WF, PPT, 
and CWU calculations performed in steps 8-10. Here, the relation is the attribute table from a
shapefile of California county political boundaries. Attributes include: county index, name, and
corresponding DWR hydrologic region.

`ca.counties` contains the shapefile, on which `roi.table` is based.

`ca.hr` contains the shapefile of DWR hydrologic regions, for California.

`wf.master.wyear` contains annual sums of cwr, ppt, etc, wf, and harvested tons/acres/USD 
aggregrated by crop, county, and water year. It only includes the counties that have corresponding 
entries in the County Ag Comissioners (CAC) annual yield reports. Counties that had modeled ag 
production, without an accompanying entry in the CAC annual reports were omitted.

`wf.master.cyear` contains the above, except aggregrated by calendar year (instead of water year). 
This data set includes the extra year of 2007.

`yield.master` contains all of the statistics reported by the CAC annual reports (production tons, 
harvested acres, value in USD), for the modeled crops.

```{r importData, message=FALSE, warning=FALSE, include=FALSE}
cdl.table <- read_csv("input/TABLES/cdl_crops.csv")
roi.table <- read_csv("input/SHAPEFILES/cnty24k09_poly/cnty24k09_poly_attributes.csv")
ca.counties <- readOGR("input/SHAPEFILES/cnty24k09_poly/cnty24k09_poly_simple.shp")
ca.hr <- readOGR("input/SHAPEFILES/dwr/dwr_hydrologic_regions.shp")
wf.master.cyear <- readRDS("output/wfs/wf_total_cyr.rds")
wf.master.wyear <- readRDS("output/wfs/wf_total_wyr.rds")
yield.master <- read_csv("output/yields/NASS_summarized_bycounty.csv")
```

## Create some functions for commonly used summary statistics

Typially in a boxplot, outliers are marked as values that fall outside of 1.5 times the interquartile range 
avove and below the 25% and 75% quantiles. `is_extreme()` is a function that we define below, that applys the
same criteria and returns TRUE if the value is a suspected outlier/extreme falue, and false otherwise.

```{r summaryFuns}
is_extreme <- function(series) {
  #' Tags values in a series according to whether or not they would appear as oulier points
  #` in a Tukey boxplot (values that lie outside of the H-spread.)
  #` Specifically, these are values that are less or greater than the 1st and 3rd quartiles
  #` plus 1.5 times the interquartile range.
  #' @param series Vector of type numeric (int or double)
  #' @return Vector of type logical, TRUE if the value is an outlier, FALSE if it is not
  return(series < (quantile(series, 0.25) - (1.5 * IQR(series)) ) | series > (quantile(series, 0.75) + (1.5 * IQR(series)) ))
}
```

## Clean erronious observations

Here, we clean obviously erronious observations.

I think the 2009 Riverside CAC survey severly under-reports the "Oats" category to the point that
it makes the "Oats" water footprint blow up (several orders of magnitude higher than baseline, see
the by-year summary notebook).

```{r cleanData}
wf.master.wyear <- wf.master.wyear %>%
  filter(!(`cdl.name` == "Oats" & `County` == "Riverside" & `Year` == 2009))
```

# C1: Average statewide water demand *for all* years, by crop

Here, we sum all daily volumes of cwr, ppt, et, and wf by crop, over each calendar and water year.
Then, we average all of the yearly sums, to produce an "average year" value, for each parameter.
```{r calc1}
wf.master.bycounty.cyear <- wf.master.cyear %>%
  mutate(Year = as.Date(sprintf("%s-01-01", Year), format="%F")) %>%
  group_by(roi.index, County, Year) %>%
  summarize_at(vars(cwr, ppt, et.b, et.g, wf.b, wf.g), funs(sum(., na.rm = TRUE))) %>%
  left_join(roi.table %>% select(NUM,`HR_NAME`),
            by = c("roi.index" = "NUM")) %>%
  ungroup() %>%         # I'm not sure what to think about the expicit `ungroup()`
  `attr<-`("year_type", "calendar") %>%
  `attr<-`("summary_type", "total")

wf.master.bycounty.wyear <- wf.master.wyear %>%
  mutate(Year = as.Date(sprintf("%s-01-01", Year), format="%F")) %>%
  group_by(roi.index, County, Year) %>%
  summarize_at(vars(cwr, ppt, et.b, et.g, wf.b, wf.g), funs(sum(., na.rm = TRUE))) %>%
  left_join(roi.table %>% select(NUM,`HR_NAME`),
            by = c("roi.index" = "NUM")) %>%
  ungroup() %>%
  `attr<-`("year_type", "water") %>%
  `attr<-`("summary_type", "total")

wf.master.byHR.wyear <- wf.master.wyear %>%
  left_join(roi.table %>% 
              select(NUM,`HR_NAME`),
            by = c("roi.index" = "NUM")) %>%
  mutate(Year = as.Date(sprintf("%s-01-01", Year), format="%F")) %>%
  group_by(`HR_NAME`, Year) %>%
  summarize_at(vars(cwr, ppt, et.b, et.g, wf.b, wf.g), funs(sum(., na.rm = TRUE))) %>%
  ungroup() %>%
  `attr<-`("year_type", "water") %>%
  `attr<-`("summary_type", "total") %>%
  `attr<-`("summarized_by", "DWR-HR")
``` 

# P1: Annual Blue WF, CWR, and PPT, county-wise

It appears that there are a fair number of counties that are significantly greater than the median
$WF_{blue}$. The second plot identifies some of these counties by labling the top 99th percentile 
counties by $WF_{blue}$. Note that we're tagging entries in the top 99% *per year*, not the top 
99% overall.

```{r plot1}
# local({
  # wfb <-
  wf.master.bycounty.wyear %>%
    ggplot() +
    geom_point(mapping = aes(x = Year, y = wf.b, color = County)) +
    scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
    labs(title = "Annual WF by county for 2007 - 2015 calendar years",
         x = "Calendar Year", y = "Annual Blue WF (m3/tonne)", 
         color = "County Name") +
    theme(legend.position = "bottom", legend.spacing.x=unit(1,"line"),
          legend.title = element_blank(), legend.key.size = unit(.5, 'lines'),
          legend.direction = 'horizontal', legend.key.width=unit(3,"line")) +
    theme(axis.text.y = element_text(angle = 90))

  # wfb.labeled <
  wf.master.bycounty.wyear %>%
    group_by(Year) %>%
    mutate(percentile = percent_rank(wf.b)) %>%
    ggplot() +
    geom_point(mapping = aes(x = Year, y = wf.b, color = County)) +
    geom_label_repel(mapping = aes(x = Year, y = wf.b, 
                                   label = ifelse(percentile > 0.99, County, NA), 
                                   fill = County), 
                     color = "white", segment.color = 'grey', box.padding = unit(0.35, "lines"), 
                     point.padding = unit(0.5, "lines"), na.rm = TRUE) +
    scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
    labs(title = "Annualv WF by county for 2008 - 2015 water years",
         subtitle = "Top 1% (per year) WF counties labled",
         x = "Water Year", y = "Annual Blue WF (m3/tonne)", 
         color = "County Name") +
    guides(fill = "none", color = "none") +
    theme(axis.text.y = element_text(angle = 90))

  # cwr.labeled <
  wf.master.bycounty.wyear %>%
    group_by(Year) %>%
    mutate(percentile = percent_rank(cwr)) %>%
    ggplot() +
    geom_point(mapping = aes(x = Year, y = cwr, color = County)) +
    geom_label_repel(mapping = aes(x = Year, y = cwr, 
                                   label = ifelse(percentile > 0.95, County, NA), 
                                   fill = County), 
                     color = "white", segment.color = 'grey', box.padding = unit(0.35, "lines"), 
                     point.padding = unit(0.5, "lines"), na.rm = TRUE) +
    scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
    labs(title = "Annual CWR by county for 2008 - 2015 water years",
         subtitle = "Top 5% (per year) CWR counties labled",
         x = "Water Year", y = "Annual CWR (m3)", 
         color = "County Name") +
    guides(fill = "none", color = "none") +
    theme(axis.text.y = element_text(angle = 90))

  # ppt.labeled <
  wf.master.bycounty.wyear %>%
    group_by(Year) %>%
    mutate(percentile = percent_rank(ppt)) %>%
    ggplot() +
    geom_point(mapping = aes(x = Year, y = ppt, color = County)) +
    geom_label_repel(mapping = aes(x = Year, y = ppt, 
                                   label = ifelse(percentile > 0.97, County, NA), 
                                   fill = County), 
                     color = "white", segment.color = 'grey', box.padding = unit(0.35, "lines"), 
                     point.padding = unit(0.5, "lines"), na.rm = TRUE) +
    scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
    labs(title = "Annual precipitation by county for 2008 - 2015 water years",
         subtitle = "Top 3% (per year) PPT counties labled",
         x = "Water Year", y = "Annual PPT (m3)", 
         color = "County Name") +
    guides(fill = "none", color = "none") +
    theme(axis.text.y = element_text(angle = 90))
  
  #plot_grid(arrangeGrob(wfb_vs_wfg, etb_vs_etg, ncol=1), nrow = 1)
# })
```

# P2: Annual Blue WF, CWR, and PPT, county-wise w/ Hydrologic Regions

We can also group counties by a classification based on location. Here, we are using regional
classifications that align with the major drainage basins of California. These `Hydrologic Regions`
correspond to drainage basins that are used for a variety of planning purposes and DWR programs,
including the CA Water plan.

On the right, we use a log/log plot in order to examine the structure of counties on the low-end of WF,
since a few, high-WF counties greately influence the scale.

```{r plot2}
local({
  
wfb_icc <- wf.master.byHR.wyear %>%
  ggplot() +
  geom_point(mapping = aes(x = Year, y = wf.b, color = HR_NAME)) +
  geom_line(mapping = aes(x = Year, y = wf.b, color = HR_NAME)) +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
  scale_y_continuous(labels = scales::comma) +
  labs(title = "Annual Blue WF by county for 2008 - 2015 water years",
       x = "Water Year", y = "Annual Blue WF (m3/tonne)", 
       color = "County Name") +
  theme(axis.text.y = element_text(angle = 90), legend.position="none") +
   theme(legend.position = "none")

wfb_icc_log <- wf.master.byHR.wyear %>%
  ggplot() +
  geom_point(mapping = aes(x = Year, y = wf.b, color = HR_NAME)) +
  geom_line(mapping = aes(x = Year, y = wf.b, color = HR_NAME)) +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
  scale_y_continuous(trans = "log10", labels = scales::comma,
                     breaks = scales::trans_breaks("log10", function(x) 10^x)) +
  annotation_logticks() +
  labs(title = "Annual Blue WF by county for 2008 - 2015 water years",
       subtitle = ("Log 10 scale"),
       x = "Water Year", y = "Annual Blue WF (m3/tonne)", 
       color = "County Name") +
  theme(axis.text.y = element_text(angle = 90), legend.position="none") +
  guides(line = "none") +
  theme(legend.position = "none")

  l1 <- get_legend(wfb_icc + guides(color = guide_legend()) + 
                   theme(legend.position="bottom", legend.spacing.x=unit(1,"line"),
                         legend.key.size = unit(.5, 'lines')))

  plot_grid(arrangeGrob(wfb_icc, wfb_icc_log, ncol=2), l1, ncol = 1, rel_heights = c(1, .1))
})
```
# P2.5: CWR and PPT w/ Hydrologic Regions
```{r plot2-5}
local({
  
cwr_icc <- wf.master.byHR.wyear %>%
  ggplot() +
  geom_point(mapping = aes(x = Year, y = cwr, color = HR_NAME)) +
  geom_line(mapping = aes(x = Year, y = cwr, color = HR_NAME)) +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
  scale_y_continuous(labels = scales::comma) +
  labs(title = "Annual CWR by county for 2008 - 2015 water years",
       x = "Water Year", y = "Annual CWR (m3)", 
       color = "County Name") +
  theme(axis.text.y = element_text(angle = 90), legend.position="none") +
   theme(legend.position = "none")

cwr_icc_log <- wf.master.byHR.wyear %>%
  ggplot() +
  geom_point(mapping = aes(x = Year, y = cwr, color = HR_NAME)) +
  geom_line(mapping = aes(x = Year, y = cwr, color = HR_NAME)) +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
  scale_y_continuous(trans = "log10", labels = scales::comma,
                     breaks = scales::trans_breaks("log10", function(x) 10^x)) +
  annotation_logticks() +
  labs(title = "Annual CWR by county for 2008 - 2015 water years",
       subtitle = ("Log 10 scale"),
       x = "Water Year", y = "Annual CWR (m3)", 
       color = "County Name") +
  theme(axis.text.y = element_text(angle = 90), legend.position="none") +
  guides(line = "none") +
  theme(legend.position = "none")

  l1 <- get_legend(cwr_icc + guides(color = guide_legend()) + 
                   theme(legend.position="bottom", legend.spacing.x=unit(1,"line"),
                         legend.key.size = unit(.5, 'lines')))

  plot_grid(arrangeGrob(cwr_icc, cwr_icc_log, ncol=2), l1, ncol = 1, rel_heights = c(1, .1))
})

local({
  
ppt_icc <- wf.master.byHR.wyear %>%
  ggplot() +
  geom_point(mapping = aes(x = Year, y = ppt, color = HR_NAME)) +
  geom_line(mapping = aes(x = Year, y = ppt, color = HR_NAME)) +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
  scale_y_continuous(labels = scales::comma) +
  labs(title = "Annual PPT by county for 2008 - 2015 water years",
       x = "Water Year", y = "Annual PPT (m3)", 
       color = "County Name") +
  theme(axis.text.y = element_text(angle = 90), legend.position="none") +
   theme(legend.position = "none")

ppt_icc_log <- wf.master.byHR.wyear %>%
  ggplot() +
  geom_point(mapping = aes(x = Year, y = ppt, color = HR_NAME)) +
  geom_line(mapping = aes(x = Year, y = ppt, color = HR_NAME)) +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
  scale_y_continuous(trans = "log10", labels = scales::comma,
                     breaks = scales::trans_breaks("log10", function(x) 10^x)) +
  annotation_logticks() +
  labs(title = "Annual PPT by county for 2008 - 2015 water years",
       subtitle = ("Log 10 scale"),
       x = "Water Year", y = "Annual PPT (m3)", 
       color = "County Name") +
  theme(axis.text.y = element_text(angle = 90), legend.position="none") +
  guides(line = "none") +
  theme(legend.position = "none")

  l1 <- get_legend(ppt_icc + guides(color = guide_legend()) + 
                   theme(legend.position="bottom", legend.spacing.x=unit(1,"line"),
                         legend.key.size = unit(.5, 'lines')))

  plot_grid(arrangeGrob(ppt_icc, ppt_icc_log, ncol=2), l1, ncol = 1, rel_heights = c(1, .1))
})
```

# P3: Annual Blue WF, CWR by Hydrologic Regions

We can also separate counties by their hydrologic region, to view similar graphs on their own scale.

```{r plot3}
wf.master.bycounty.wyear %>%
  ggplot() +
  geom_point(mapping = aes(x = Year, y = wf.b, color = County)) +
  facet_wrap(~HR_NAME, ncol = 3, scales = "free") +
  geom_line(mapping = aes(x = Year, y = wf.b, color = County)) +
  geom_label_repel(mapping = aes(x = Year, y = wf.b, 
                                 label = ifelse(Year == max(wf.master.bycounty.wyear[["Year"]])%m-% months(12),County,NA), 
                                 color = County), 
                   box.padding = unit(0.25, "lines"), 
                   point.padding = unit(0.4, "lines"), nudge_x = 35, na.rm = TRUE, size = 2) +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
  scale_y_continuous(labels = scales::comma) +
  expand_limits(x = as.Date("2016-01-01")) +
  labs(title = "Annual Blue WF by county for 2008 - 2015 water years",
      x = "Water Year", y = "Annual Blue WF  (m3/tonne)", 
      color = "County Name") +
  theme(axis.text.y = element_text(angle = 90), legend.position="none") +
  guides(fill = "none")

wf.master.bycounty.wyear %>%
  ggplot() +
  geom_point(mapping = aes(x = Year, y = cwr, color = County)) +
  facet_wrap(~HR_NAME, ncol = 3, scales = "free") +
  geom_line(mapping = aes(x = Year, y = cwr, color = County)) +
  geom_label_repel(mapping = aes(x = Year, y = cwr, 
                                 label = ifelse(Year == max(wf.master.bycounty.wyear[["Year"]])%m-% months(12),County,NA), 
                                 color = County), 
                   box.padding = unit(0.25, "lines"), 
                   point.padding = unit(0.4, "lines"), nudge_x = 35, na.rm = TRUE, size = 2) +
  scale_x_date(date_breaks = "1 years", date_labels = "%Y") +
  scale_y_continuous(labels = scales::comma) +
  expand_limits(x = as.Date("2016-01-01")) +
  labs(title = "Annual CWR by county for 2008 - 2015 water years",
      x = "Water Year", y = "Annual Crop Water Requirement (m3)", 
      color = "County Name") +
  theme(axis.text.y = element_text(angle = 90), legend.position="none") +
  guides(fill = "none")
```