---
title: "County Aggregations"
author: "asmtry"
output: 
  html_document: 
    number_sections: yes
    code_folding: hide
    theme: readable
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setupKnitr, include = FALSE}
knitr::opts_knit$set(echo = TRUE, collapse = TRUE)
# knitr::opts_chunk$set(cache = TRUE, autodep = TRUE,
#                       cache.path = paste0('cache/',sub(".Rmd", "", knitr::current_input()),'/'),
#                       fig.path = paste0('figures/',sub(".Rmd", "", knitr::current_input()),'/'))
knitr::opts_chunk$set(fig.width=8, fig.asp = 0.618, warning = FALSE)
options(width = 120)
```

# Setup
This worksheet leans heavily on `tidyverse` packages.

```{r setupEnv, include=FALSE}
source("R/utilities.R")
source("R/kc.R")
source("R/eto.R")

pkgTest("tidyverse", "rgdal", "raster", "tools", "lubridate", "parallel")
rasterOptions(progress = "text", tmpdir = "tmpdir", time = TRUE)
# rasterOptions(todisk = TRUE)
# rasterOptions(progress = "text", tmpdir = "tmpdir", time = TRUE)
ggplot2::theme_set(theme_bw())
```

## Import data

`lc.dir` contains the Cropland Data Layer files that have been reprojected and upscaled
(when nessary). These are the files that are used in the final analysis.

`cdl.table` contains relations between crops, their index number in the Cropland Data Layer,
and the corresponding name and index number in the FAO Indicative Crop Classification (ICC 1.1).

`roi.table` contains relations from the regions of interest used to aggregrate the WF, PPT, 
and CWU calculations performed in steps 8-10. Here, the relation is the attribute table from a
shapefile of California county political boundaries. Attributes include: county index, name, and
corresponding DWR hydrologic region.

`ca.counties` contains the shapefile, on which `roi.table` is based.

`ca.hr` contains the shapefile of DWR hydrologic regions, for California.

`yield.master` contains all of the statistics reported by the CAC annual reports (production tons, 
harvested acres, value in USD), for the modeled crops.

```{r importData, message=FALSE, warning=FALSE, include=FALSE}
lc.dir <- "output/cleaned_inputs/CDL_CA_projected"
cdl.table <- read_csv("input/TABLES/cdl_crops.csv")
roi.table <- read_csv("output/ca_counties_attributes.csv")
ca.counties <- readOGR("input/SHAPEFILES/cnty24k09_poly/cnty24k09_poly_s100.shp")
ca.hr <- readOGR("input/SHAPEFILES/dwr/dwr_hydrologic_regions.shp")
yield.master <-  read_csv("output/yields/NASS_summarized_bycounty.csv", 
                          col_types = cols(hvst.acres = col_double(), 
                                           prod.tons = col_double(), val.usd = col_double()))
```

```{r prepareAnalysis}
lc.calc.exists <- TRUE

if (lc.calc.exists) {
  cdl.freqs <- read_csv("output/tmp/mcd_cdl_freq.csv")
} else {

  lc.paths <- list.files(path=lc.dir, pattern=".(tif)$", full.names=T, recursive=TRUE)
  
  lc.table <- data.frame(
    abs_path = lc.paths,
    source = sapply(strsplit(file_path_sans_ext(lc.paths),"/"),'[[',3),
    product_name = 'CDL',
    date = as.Date(sprintf("%s-01-01",sapply(strsplit(file_path_sans_ext(lc.paths),"/"),'[[',4)), format="%F"),
    stringsAsFactors = FALSE
  )
  
  lc.table <- lc.table %>%
    dplyr::filter(date != as.Date("2007-01-01")) %>% 
    dplyr::filter(date != as.Date("2016-01-01"))
}

```

Takes about 40 min on bootsy.
```{r}
if (lc.calc.exists) {
  cdl.freqs <- read_csv("output/tmp/mcd_cdl_freq.csv")
} else {
  crop_mask_freq <- function(target.path) {
    target.county <- ca.counties[ca.counties@data$NAME_UCASE == "MERCED",]
    raster(target.path) %>%
      raster::crop(target.county) %>%
      raster::mask(target.county) %>%
      raster::freq %>%
      as.data.frame %>%
      return
  }
  
  freqs <- lc.table %>%
    dplyr::pull(abs_path) %>%
    purrr::map(crop_mask_freq) %>%
    purrr::reduce(full_join, by = "value") %>%
    dplyr::arrange(value)
  
  freqs %>%
    purrr::set_names(c("cdl.value",2008:2015)) %>%
    tidyr::gather(year, cdl.cells, -cdl.value) %>%
    mutate(cdl.sq.m = cdl.cells * 30 * 30) %>%
    mutate(cdl.acres = round(cdl.sq.m / 4046.87261)) %>% 
    write_csv("output/tmp/mcd_cdl_freq.csv")
}
```

# Compare to CAC
```{r}
yield.master <- read_csv("output/yields/NASS_summarized_bycounty.csv") %>%
    filter(County == "Merced") %>%
    filter(Year >= 2008 & Year <= 2015) %>%
    full_join(cdl.freqs, by = c("cdl.value","Year" = "year"))
```

